\documentclass[
  journal=,
  manuscript=article,  %% article (default), rescience, data, software, proceedings, poster
  layout=preprint,  %% preprint (for submission) or publish (for publisher only)
  year=2025,
%  volume=x,
]{extra/joas}
\usepackage{xeCJK}
\usepackage{biblatex}
\usepackage{cleveref}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{csquotes}
\MakeOuterQuote{"}
\renewcommand{\abstractname}{Abstract}
\renewcommand{\figurename}{Figure}
\renewcommand{\tablename}{Table}
\renewcommand{\refname}{References}
\crefname{appendix}{Appendix}{Appendices}
\interfootnotelinepenalty=10000
\addbibresource{references.bib}
\DeclareNameAlias{sortname}{family-given}
\DeclareNameAlias{default}{family-given}

\linespread{1.0}

\usepackage{lineno}
\nolinenumbers

\title{A Rationalist Road of Understanding Gender Identity: an Autoethnography of a Transgender Evolutionary Biologist}

\author{Jiao Sun\orcidlink{0000-0002-5028-8132}}
\affiliation{Division of Ecology and Evolutionary Biology, School of Biological Science, University of Reading, Whiteknights, Reading, RG6 6EX, United Kingdom}
\email{j.sun@pgr.reading.ac.uk}
\date{10/02/2025}

% maximum five keywords
\keywords{Autoethnography, gender abolitionism, gender identity, gender studies, philosophy of biology, post-structuralism, trans philosophy}

% Important: don't overuse abbreviations. Only use abbreviations if the term is used more than ten times throughout the paper. Otherwise, write them in full.
%\abbreviations{}

\begin{document}

%\maketitle

\begin{abstract}
This autoethnography presents a comprehensive personal journey of a transgender evolutionary biologist examining the origins of their gender identity, finally culminating in an argument for gender abolitionism. The author's ``gender identity'' is not to an innate, ontological essence, but to a complex synthesis of internalised social norms, childhood trauma, aesthetic preferences, and reactions to a ``pervasively gendered'' society that repeatedly assigned gendered meaning to neutral behaviours, objects, and personality traits.

The narrative critically engages with mainstream gender theories, revealing logical inconsistencies, circular reasoning, and category errors within concepts such as the sex/gender distinction, ``innate gender identity'', ``assigned sex at birth'' (ASAB), and the cisgender/transgender binary. The author proposes a revolution in the form of gender abolitionism: a framework that strictly limits sex \textit{sensu stricto} to gametes, dismantles phenotypic ``sex'' into a spectrum of sexual dimorphic traits, and advocates for the complete removal of gender as a social, legal, cultural, and self-identity category.

Furthermore, the article extends its critique to post-structuralist and queer theories, arguing that while their deconstructive intentions are noted, their real-world effect paradoxically reinforces gender-centrism and destructed an intersubjective world, ultimately failing to provide a path to liberation. Ultimately, the work is a defence of universalism and scientific realism as essential tools for dismantling all forms of oppression, arguing that a consistent application of reason offers the most profound and inclusive path toward human freedom, transcending the contemporary identity politics.
\end{abstract}

\addcontentsline{toc}{section}{Abstract}

\section{Introduction}\label{sec:introduction}
\input{.archive/introduction}

\section{My Experience}\label{sec:my-experience}
\input{.archive/experience}

\section{My Gender Identity}\label{subsec:my-gender-identity}
\input{appendices/my-gender-identity}

%\section{Vertigo}\{sec:vertigo}
%\input{chapters/vertigo}

%\subsection{My Philosophy}\label{subsec:my-philosophy}
%\input{chapters/my-philosophy}

%\section{Philosophical Critique of Gender Identity}\label{sec:philosophical-critique}
%\input{chapters/philosophical-critique}

%\section{For Abolition}\label{sec:for-abolition}
%\input{chapters/for-abolition}

%\section{Dialogues}\label{sec:dialogues}

%\subsection{Dialogue with Gender pluralism}\label{subsec:dialogue-with-gender-pluralism}
%\input{chapters/dialogue-with-pluralism}

%\subsection{Dialogue with Queer Theory}\label{subsec:dialogue-with-queer-theory}
%\input{chapters/dialogue-with-queer}

\section{Dialogue with Post-Structuralism}\label{sec:dialogue-with-post-structuralism}
\input{chapters/dialogue-with-post-structuralism}

%\subsection{Dialogue with the world}
%\input{chapters/dialogue-with-the-world}

%\section{Enabling Act}\label{sec:enabling-act}
%\input{chapters/enabling-act}

%\section{An Answer to the Question: What is Enlightenment?}\label{sec:what-is-enlightenment}
%\input{.archive/.what-is-enlightenment}

%\section{Conclusion}\label{sec:conclusion}
%\input{chapters/conclusion}

\section{Postscript: meta-ethnography behind the autoethnography}\label{sec:postscript:-meta-ethnography-behind-the-autoethnography}
\input{chapters/postscript}

\paragraph*{Acknowledgements}

I am grateful to the Enlightenment and its thinkers. You illuminated the darkness with the light of reason. You constructed the independent, resilient, courageous, and fearless subject. I am sincerely grateful to the anonymous prisoner in Mauthausen concentration camp. You kept the immortal light of the Enlightenment and Haskalah. You proved how invincible and indestructible humanity can be, even in the most dehumanising situation. I am extremely grateful to the little girl in red shoes for her courage in facing the bullies. His small shield has become an impregnable shelter that protects them from any irrational violence.

{\centering
        {\large Long live the Enlightenment!}
}

\paragraph*{Positionality statement}

JS is a human being (\textit{Homo sapiens} {\small \textsc{Linnaeus}, 1758}). They live on Earth in the Holocene. Their reason helps them understand the objective world and other human beings.

%\section*{Source Code Availability}
%
%Code for generating this document and visualising the author's ``bundle of gender identity'' (\cref{fig:bundle}): \url{https://github.com/sun-jiao/autoethnography}

\printbibliography

\newpage

\appendix

\crefalias{section}{appendix}

{\large \textsc{Appendices}}

%\section[“Assigned Sex at Birth” Lacks Inclusivity for Intersex People, and a Philosophical Critique of its “Mechanical Idealism”]{``Assigned Sex at Birth'' Lacks Inclusivity for Intersex People, and a Philosophical Critique of its ``Mechanical Idealism''} \label{app:asab}
%\input{appendices/assigned-sex-at-birth-and-intersex}

\begin{refsection}
    \section{An Autoethnography of Interpellation and Performativity}\label{app:ps-aeb}
    \counterwithin{figure}{section}
    \setcounter{figure}{0}
    \counterwithin{table}{section}
    \setcounter{table}{0}
    \setcounter{footnote}{0}
    \input{appendices/becoming-woman}
    \printbibliography[heading=subbibliography]
\end{refsection}

\end{document}

%\newpage
%
%\appendix
%
%{\large \textsc{Appendices}}
%
%\crefalias{section}{appendix}
%
%\end{document}
