\documentclass[
  journal=PREPRINT,
  manuscript=article,  %% article (default), rescience, data, software, proceedings, poster
  layout=preprint,  %% preprint (for submission) or publish (for publisher only)
  year=,
  volume=,
]{extra/joas}
%\doi{10.13140/RG.2.2.27723.66085}
%\received {1 Sep 2025}
%\revised  {1 Dec 2025}
%\accepted {10 Dec 2025}
%\published{20 Dec 2025}
%\editor{Joanna Thorne}
%\reviewers{Anonymous reviewers}

\usepackage[backend=biber, style=apa, sorting=nyt]{biblatex}
\usepackage{cleveref}
\usepackage{hyperref}
\usepackage{csquotes}
\MakeOuterQuote{"}
\renewcommand{\abstractname}{Abstract}
\renewcommand{\figurename}{Figure}
\renewcommand{\tablename}{Table}
\renewcommand{\refname}{References}
\addbibresource{references.bib}
\DeclareNameAlias{sortname}{family-given}
\DeclareNameAlias{default}{family-given}

\providecommand{\posscite}[1]{\citeauthor{#1}'s (\citeyear{#1})}
\usepackage{lineno}
\nolinenumbers

\title{Applying the predictive coding theory to gender identity}

\author{Jiao Sun\orcidlink{0000-0002-5028-8132}}
\affiliation{Division of Ecology and Evolutionary Biology, School of Biological Science, University of Reading, Whiteknights, Reading, RG6 6EX, United Kingdom}
\email{j.sun@pgr.reading.ac.uk}
\date{12/01/2026}

\keywords{Gender identity, philosophy of biology, philosophy of mind, sex/gender distinction}

\begin{document}

\maketitle

\begin{abstract}
The discourse on gender identity is currently polarised between biological essentialism, which posits an innate, fixed essence, and post-structuralist queer theory, which views gender as a purely social performance. This paper critiques both frameworks by first dismantling the concept of "phenotypic sex," arguing that it involves the fallacy of begging the question and constitutes a scientific redundancy; biological sex should be strictly limited to gametes, while other traits are merely sexual dimorphisms. Subsequently, I challenge the neuro-essentialist notion of a "male" or "female" brain, proposing instead that gender identity emerges through the brain's predictive coding mechanism. Under this framework, the brain updates its internal self-model to minimise prediction errors arising from the incongruence between "raw feelings" -- stemming from body representation, sensory processing (e.g., in autism), or social trauma -- and assigned gender categories. This model resolves the tension between biological reality and social construction, characterising gender identity not as a metaphysical essence but as a post-hoc rationalisation. Finally, the political implications are discussed: by dismantling "phenotypic sex" and adopting a predictive processing model, we can demystify gender identity, stripping it of oppressive essentialism while providing a robust materialist explanation for transgender experiences.
\end{abstract}

\addcontentsline{toc}{section}{Abstract}

\section{Introduction}

The contemporary intellectual landscape surrounding gender is dominated by two primary, often contending, theoretical frameworks: biological essentialism and post-structuralist queer theory. The former frequently posits ``gender identity'' as an inherent essence \parencite{APA2015Guidelines, NHS2022Gender}. This perspective, often adopting a ``born this way'' narrative, attempts to anchor social identity in the brain, a view supported by some neurologists. Conversely, post-structuralism, exemplified by the work of \textcite{Butler1990Gender}, approaches gender as a socially constructed and performative phenomenon, denying any objective understanding of pre-discursive biological reality. However, while essentialism struggles to account for neuroplasticity and the complexity of abstract concepts, strict social constructionism often fails to integrate the material reality of body representation and the "raw feelings" reported by transgender individuals. In this article, I propose a synthesis using the framework of predictive coding. I argue that "gender identity" is neither a genetic inevitability nor a purely linguistic performance, but a cognitive solution generated by the brain to resolve prediction errors. To establish this, I will first deconstruct the definition of "biological sex," demonstrating its scientific redundancy when applied beyond gametes. Subsequently, I will review neurological evidence to show how the predictive brain integrates sensory data, including interoceptive signals and social cues, to construct a gendered self-model.

\section{Dismantling "sex"}
\input{chapters/dismantling-sex.tex}

\section{Neurology on Gender Identity}
\input{chapters/biological-critique}

\section{Discussion}

In this section, I will discuss the political effect of the aforementioned dismantling of sex and the predictive coding model of gender identity. 

The dismantling of sex disarms conservatives who continuously misinterpret and misappropriate biological knowledge. If you like gametes, then let's talk about gametes. I completely agree that "sex is only about gametes" \parencite{Lehtonen2014Gamete, Goymann2023Biological, Hurst1996There, Griffiths2025Biology}. However, conservatives still rely on the phenotypic sex in practice, which is self-contradictory. 

By biologically confining sex strictly to an unobservable trait, it cannot be ``assigned'' or ``inferred.'' \textcite{Parvin1982Ovulation} reported a person who was completely ``phenotypic male'' and had fathered a daughter, but one of their two ``testicles'' was actually a pure ovary (not an ovotestis), and dissection showed it had previously ovulated. Therefore, most people, even those who have biological children, cannot know for sure if they are capable of producing two types of gametes. This makes it lose any possibility of being used for social classification and oppression. It becomes a boring technical term of reproductive biology, completely ``exiled'' from everyday language and the operation of power. Under this framework, sexual dimorphism is a dynamic spectrum that constantly changes throughout evolutionary history. The so-called ``phenotypic sex'' should be dismantled into a series of discrete, decentralised phenotypic traits such as chromosomes, hormones, as well as all morphology and anatomical traits. They are on the sexual dimorphism spectrum, along with sexual dimorphic traits not traditionally classified as ``phenotypic sex'', like height, weight, body hair, and body fat percentage \parencite{Wells2007Sexual}. 

This fallacy is manifested even in some conservative scientists, like \textcite{Sokal2024Sex}, who claim that sex is an ``objective biological reality,'' ``determined at conception and observed at birth.'' I agree that the gametic sex is an objective biological reality, and is strictly binary in Vertebrata. While according to \textcite{Jones2006Gamete}, ``Conception occurs when a sperm and an ovum fuse to become a zygote.'' ``The process of fertilisation, or conception, involves fusion of the nucleus of a male gamete (sperm) and a female gamete (ovum) to form a new individual.'' At ``conception'' (fertilisation), it is just a zygote, a single cell. It does not have gametic sex because it cannot produce its own gametes, nor does it have phenotypic sex by lacking a developed body. Even if its genome guides it to develop into a "typical" male or female under normal conditions, it will not necessarily be so. For instance, if a 46, XY zygote loses its Y chromosome during the first mitotic division after fertilisation, it will develop into a 45, X0/46, XY chimaera (mixed gonadal dysgenesis) or a 45, X0 individual with Turner syndrome \parencite{Gravholt2017Clinical, Jacobs1997Turner, Lopes2014Mosaicism}.

The predictive coding model liberates us by eliminating the intellectual barriers, which I, as a transgender (non-binary) doctoral student in biology, encountered when starting exploring my gender identity, such as: What is gender identity? What is its relationship to ``gender''? The term ``gender'' refers to a sociocultural norm, then it is essentially an identity with a social construct. This contradicts the so-called ``innate, profound feeling,'' because social norms cannot be innate. It is also politically problematic, as it seems that I self-identify with the oppressive gender roles. "A woman is a person who self identifies as a woman" constitutes a ridiculous tautology. I felt it very mystical and obscurantist. I consulted a few transgender communities on some platforms, including Reddit, RedNote (Xiaohongshu) and Zhihu (a Chinese Q\&A website), hoping for some advice or help. However, almost no one understood my question and responded to me seriously. I was insulted or degraded on all three platforms, being labelled with many ridiculous terms, namely ``gender essentialism'', ``Landian accelerationism'', "internalised transphobia" or ``solipsism'', and my account was banned on Reddit. 

Providing a clear, scientifically reasonable, and logically consistent theory helps transgender individuals. After the aforementioned conflict, I read some neurological articles and used the predictive coding model to understand my gender identity. I believe that my own gender identity is a product of childhood trauma, bullying, misnaming, romantic feeling and physiological diseases. Under the predictive coding framework, these disparate, painful, and confusing raw experiences created a persistent state of high entropy or prediction error within my cognitive system. The "cisgender male" category failed to predict or explain these sensory and emotional inputs. Consequently, my brain adopted a non-binary/transgender identity as a higher-level hypothesis that successfully minimised this error, binding these traumatic and physiological fragments into a coherent narrative of self. This realisation does not invalidate my identity; rather, it demystifies it.

This reminds me of Baruch Spinoza's words: ``\textit{Non ridere, non lugere, neque detestari, sed intelligere}'' (not to ridicule, not to lament, not to detest, but to understand). By moving away from the search for a "transgender essence" or a "wrong body" narrative, we can approach gender identity with the analytical clarity Spinoza advocated. We need not "lament" the lack of a "female body," nor "detest" the biological reality of our development. Instead, we must "understand" the precise mechanisms by which our neurobiology and environment interact to produce our identity. This materialist understanding liberates us from the burden of proving our validity through metaphysical claims, allowing us to view our gender as a functional, adaptive, and necessary configuration of our consciousness.

\section{Conclusion}

In this paper, I have argued for a radical restructuring of how we define sex and interpret gender identity. First, I demonstrated that the concept of "phenotypic sex" is an arbitrary and unjustified subset of sexual dimorphism that begs the question; scientific precision requires us to restrict "sex" strictly to gametes and treat all other features as variable traits on a spectrum. Second, I challenged the "innate gender identity" and "brain sex" hypotheses, showing them to be incompatible with evolutionary efficiency and neuroplasticity.  

Instead, I have established the predictive coding theory as a superior explanatory model. This framework posits that gender identity is constructed by the brain to minimise prediction errors caused by the friction between raw, pre-linguistic feelings (such as body incongruence, autistic sensory processing, or trauma) and enforced social categories. This model successfully bridges the gap between the biological reality of the brain and the social reality of gender constructs without falling into essentialism.  

Politically, this approach disarms conservative appeals to "biological reality" by revealing the fluidity of sexual dimorphism and the cognitive mechanisms of identity formation. For transgender individuals, particularly those who are neurodivergent, this theory offers a validating, demystified self-understanding that relies on cognitive necessity rather than metaphysical souls. This model needs more positivistic studies, particularly focusing on the specific neural correlates of prediction error minimisation in atypical and non-binary transgender populations, to further substantiate these theoretical claims.

\printbibliography

\end{document}