Moreover, such situations also exist in areas other than gender. Considering this is an ``autoethnography,'' let's choose the historical event discussed in my middle school language arts textbook as a case study. Just as I thought in middle school, Germany's post-war ``Vergangenheitsbewältigung'' (overcoming the past) historiography also has huge internal tensions:

Why should those former anti-Nazi heroes, Nazi victims, their families, and descendants ``reflect'' and pay taxes for Nazi war reparations? Why should new immigrants, even those from countries invaded by the Nazis, also ``reflect'' and pay taxes for Nazi war reparations? Constitutional patriotism holds that the government does not represent a specific ethnic group, culture, or history. Then it is simply a legal entity responsible for administrative affairs, employed by the people to serve them. If the people did not directly support its crimes, why should they reflect on its actions?

What is special about the state? Why is it the state (Germany) and not a higher-level political entity (the EU) or a lower-level political entity (the state of Prussia) that needs to reflect on war history? The designation of this level is socially constructed and lacks inherent, logical reason. This seems to imply that ``Germany is more likely to start another war in the future, so it must be prevented in advance,'' which cannot be proven. By limiting the scope of ``reflecting on Nazism'' to Germany, it allows other countries -- especially the United States and Israel -- to comfortably see themselves as victors or victims, thus naively believing they are ``naturally immune'' to fascism, providing spaces for fascism to return under a different name. Furthermore, Germany comfortably supports it under the absurd and irrational so-called ``special responsibility to Israel.''

Why can a person openly display the Iron Cross symbol but not the swastika? Although the use of the swastika in Germany for Buddhism and Hinduism (as well as for historical education and research) is still permitted, the Iron Cross does not have a similar restriction, like ``for military use only.'' Is this fair to Germany's East and South Asian immigrants? Both are cultural symbols with long histories that predate the Nazis. The swastika's history is even longer than the Iron Cross's, and we can even find right-turning 45° Buddhist swastikas on some ancient buildings in China. Its pre-Nazi usage was also more peaceful than the Iron Cross, which was associated with the Prussian army even before the Nazis. Is the only difference that the Iron Cross is ``German,'' while the swastika is not? The former is ``our,'' ``Deutschness'' national culture, to be cherished, saved, and purified; the latter is ``external,'' ``Other,'' ``non- Deutschness,'' can be arbitrarily defined by the Nazis, and cannot be reclaimed after being tainted by them. Does this mean that Germany is still essentially a nation-state of the German people, just claiming not to be one in words?

Why is the Iron Cross not an unconstitutional symbol? Because the Wehrmacht is not an unconstitutional organisation. Why is the Wehrmacht not an unconstitutional organisation? Because ``we'' stipulated that it is not. However, historical research shows that the Wehrmacht was far from innocent. \parencite{Wette2006Wehrmacht} This seems to be a self-fulfilling prophecy. The legislators of the Federal Republic of Germany prophesied: ``The Iron Cross can be saved and purified, while the swastika cannot.'' Then, they passed legislation allowing the unrestricted use of the Iron Cross while completely banning the swastika, ensuring that this prophecy would forever be true.

Germany's so-called ``overcoming the past'' is filled with a series of lies, self-contradictions, and doublethink.

I believe the only logically consistent solution is to execute all high-ranking leaders with leadership responsibility in the Nazi Party, concentration camps, Wehrmacht, SS, and SA, as well as grassroots members who directly killed people, as murderers. Grassroots members who did not directly kill people should be sentenced or acquitted based on their specific actions (e.g., helping the victims). The released members and the rest of the German people would live freely and without original sin in a clean Germany.

Some will say my solution is too naive. Nevertheless, this is not naivety, but the logically consistent extension of the Nuremberg trials.

Suppose we believe that international humanitarian law can be applied retroactively. In that case, we should apply it universally, extending the principle established by the Nuremberg trials to all levels of members of the Nazi party and its related organisations. Similarly, any form of international humanitarian law should also be applied retroactively. The bombing of Dresden, Tokyo, and the atomic bombings of Hiroshima and Nagasaki violated the principle of proportionality in the 1977 Additional Protocol to the Geneva Conventions. Roosevelt, Truman, and all US military personnel involved in these actions are guilty. If the international law of 1945 can be used to try crimes of 1942, why can't the international law of 1977 be used to try crimes of 1945?

By the same token, if it is said that after 70 years of aggression and occupation, Hamas killing hundreds of Israel's civilians in a war is called terrorism, let's try to extract a universal rule from this event: the invaded and occupied country cannot kill civilians of the aggressor or occupier country during its resistance to aggression and occupation, otherwise it is ``terrorism.'' As an abstract principle, I do not oppose this.

Thus, let's now apply it universally: after the United States experienced the Japanese invasion of Pearl Harbor and four years of the Pacific War, the US military killing hundreds of thousands of Japanese civilians with incendiary bombs and atomic bombs is also terrorism, and should be a more heinous form of terrorism -- state terrorism, because the order to massacre civilians came directly from the US president. In contrast, Hamas is not the legitimate government of Palestine, so Hamas's actions are just ordinary terrorism, not ``state terrorism.'' \footnote{I am not saying that Hamas killing Israel's civilians is right. There are, of course, innocent civilians who do not support Zionism, just as there were innocent civilians in Hiroshima and Nagasaki who did not support Japanese militarism. Actually, the archives of the Japanese Communist Party and Socialist Party clearly record some Japanese political prisoners who died in the atomic bombings.}

We, as I have analysed, either apply retroactivity universally or do not use retroactivity at all.

The rule of the Nazis itself was built on such self-exceptionalism, a complete betrayal of the Enlightenment spirit, reason, science, and ``daring to know.'' Questioning Nazi political propaganda with true Enlightenment reason and scientific \textit{Ethos} would absolutely not be tolerated: why are Jews (and Roma, Slavs) inferior to Germans? How can morality be quantified? Which area of the brain is related to morality? What are the anatomical differences in this brain region between morally inferior and morally superior people? How can it be proven that Jews generally have this brain structure? What selection pressures made morally inferior Jews have higher fitness and leave more offspring than morally superior Jews? When did the morality of the Jews begin to decline? During the period of the Kingdom of Israel or during the Diaspora? If it were during the Kingdom of Israel, why didn't the same selection pressures act on other Levantine peoples living in the same environment? If it was during the Jewish Diaspora, why didn't the same selection pressures act on European peoples?

Honestly, the first time I came up with the idea that ``a world that completely follows science and reason would be so free and equal'' was a question very similar to the Nazi's anti-scientific propaganda, and that question was about gender: some people say female students are not suited for science. What is the evidence? Which area of the brain is it related to? What brain structure is suitable for science? What is the relationship between these brain structures and sex? Do sex hormones promote the differentiation of brain structure in different directions in the early fetus? Was this process shaped by sexual selection? Where did the selection pressure come from? How was this hypothesis verified?

Germany's military aid to Israel's genocide crime in Gaza,~\parencite{Soussi2023War} defining the Boycott, Divestment, and Sanctions (BDS) movement and accusing Israel of genocide as so-called ``anti-Semitism''~\parencite{Kuras2023Strange, Whittle2024Germany} is also this kind of exceptionalism. The concept of ``special responsibility'' is not a universal principle; it is an exceptionalist political tool used to justify specific foreign policies. It allows Germany to hypocritically present its geopolitical actions as an inevitable ``moral'' responsibility stemming from its unique history, rather than a matter of its national geopolitical interest. If Germany has a ``special responsibility'' towards Israel because of Nazis, there is a frightening, hidden logic: ``Israel,'' a sovereign state, has an \textit{a priori} inherent relationship with Jews, an ethnic group. This is almost isomorphic with the Nazis' racial theory that claimed an \textit{a priori} relationship between Germany and ``Aryans.''

 Many early Zionists were secular Jews who received European education, who are a product of the Haskalah. However, they believed the Haskalah ideal (Jewish integration into European civilisation) was impossible and instead employed another European tool: nationalism, to attempt to establish a Jewish nation-state. The Haskalah's universalist ideal, in its own failure, transformed into its opposite: a particularist, nationalist practice. As a modern nationalist project, it employed the instrumental rationality and colonial logic. It required calculations of land, population, resources, and security, viewing non-Jewish populations (particularly Palestinians) as resources to be calculated, managed, and controlled. To achieve its instrumental rationality, Israel's national security apparatus both exploited Palestinian labour and excluded and even expelled them for the so-called ``security.'' The instrumental rationality is almost isomorphic to \textcite{Adorno1997Dialectic}'s critique in the \textit{Dialectic of Enlightenment}. Israel's occupation and blockade of Palestine can be viewed as a form of ``the Dialectic of Haskalah.'' However, Adorno himself supported Israel.

Let us take a look at what we have now:

\begin{enumerate}
    \item Conservatives who do not believe that sex is only about gametes.
    \item Richard Dawkins, who does not believe in postzygotic mutations.
    \item Liberals and gender theorists who do not believe that external assigned identity is immoral, assigning ``cisgender'' to billions of people.
    \item Emily Fairchild, a queer theorist, who does not believe in différance and dissemination.
    \item Dogmatic transgender communities which do not respect lived experiences.
    \item Queer theorists who do not consider themselves and the dogmatic transgender communities as nodes of power.
    \item Micheal Foucault, who did not believe in the discursive effects and author function, using his personal intent to debate with Habermas.
    \item The German government, which does not believe that sovereign states are not inherently related to ethnic groups, both for the Iron Cross and Israel.
    \item An international humanity law system which does not believe that humanity laws can retroactively apply.
    \item Theodor Adorno, who does not believe in the dialectic of rationality.
\end{enumerate}

The whole world is profoundly hypocritical. The situation with Germany and Israel is precisely the same as the dogmatic, exclusionary transgender communities I encountered. The problem is not the specific content of this exceptionalism (whether it's ``the living space of the Aryans,'' ``the gender order created by God,'' ``Germany's special responsibility to Israel,'' or ``lived experience''), but that it creates a zone where reason, science, empirical evidence, logical consistency, universal human rights, and justice are legitimately declared invalid, and power will ultimately do what it wants to do.

This is nothing else but a historical self-repeating of the Enabling Act of 1933. The real Enabling Act, by creating a legal ``state of exception,'' authorised the Hitler government to legislate by bypassing the constitution, thereby destroying the Weimar Republic. Every accepted ``principle of exception,'' no matter how big or small, no matter what content is in it, is a micro ``enabling act.'' It authorises power to override rules, thereby destroying the foundations of justice.

The so-called ``Germany's special responsibility to Israel'' is such an enabling act. When state actions touch upon the issue of so-called ``Israel's right to exist,'' the enabling act is activated, and regular, universalist considerations -- whether it's compliance with international law or the universal human rights of all peoples, including Palestinians -- can be legitimately suspended or downgraded.

The so-called ``lived experience'' is also such an enabling act. Its purpose is not to protect people's freedom to express their experiences, but to use this mystifying and obscurantist language to conceal its true purpose: systematically promoting a specific type of experience and devaluing other experiences.

Moreover, the sovereign state, the nation-state, and the Westphalian system are also enabling acts. Its purpose is to permanently prevent the universal implementation of fundamental human rights. Every sovereign state's constitution is also an enabling act that delineates boundaries, establishes states of exception, and promotes exceptionalism. It aims to declare that its principles are not universal. They apply only to this group of people (citizens) and not to another (foreigners).

The entire global nation-state system is equivalent to saying that the full enjoyment of human rights depends on the accidental facts of their geographical location of birth and their nationality. This cannot pass the Kantian test of universalisability. Moreover, it is not like ``it is permissible to kill another person when it is convenient for achieving one's own goals.'' $\to$ ``a rational person must will their own continued existence; to will such a world could lead to one's own destruction. This creates a conflict in the will,'' which relies on reasoning for a \textit{reductio ad absurdum}. It directly denies universalism in its very wording. It makes an entirely accidental, irrational factor (place of birth) the core of human rights, which is fundamentally contradictory to the requirement that ``a law must be universal.'' The only special aspect is that it has endured for so long that people consider it a normal state of affairs, and jurists and philosophers even regard it as a self-evident starting point for analysis.

The only way to guarantee justice and prevent tyranny is to abolish all zones of exception mercilessly. Universal laws, including fundamental human rights, must apply to everyone, everywhere, at all times.

If Germany had adopted a rationalist and universalist narrative, such as ``the disaster created by Nazi was an analysable historical event rooted in a specific historical and political-economical context; its racial theory is pseudoscience, the word Aryan refers to Iranians and has nothing to do with Germans; there is no evidence that race or ethnicity has any biological essence, Germans are neither noble nor guilty; `never again' means never again for anyone, anywhere,'' the current tragedy would not have happened.

The Nazis had destroyed Germany's rationalist tradition to such an extent that even the reflection of Nazism still remains within a mindset contaminated by it. They used a new exceptionalism (Germany's guilt and special responsibility towards Israel) to replace the old exceptionalism (Aryan superiority). It is a symptom of the profound damage that Nazism has caused to Germany's intellectual tradition. As the homeland of Kant, Germany has never truly returned to the glorious Enlightenment tradition. It continues to use a tribal, mythical, and irrational narrative to resolve an issue that can only be truly understood and overcome through the universal reason. The special responsibility is not the antidote to Nazism. It is precisely a painful, lingering aftereffect left by the Nazis' ideological virus, a ``long Nazism'' similar to the long COVID\@.

The doubt and abandonment of universal reason is not a profound reflection on Nazism. On the contrary, it is itself a manifestation of Nazism's ideological victory. The Nazis not only destroyed life but, on a spiritual level, also destroyed the trust in the only intellectual tradition that could truly falsify and resist it -- the universalism of the Enlightenment.