Critics might accuse me, ``your theory is just a wrap of queer theory with analytic and scientific languages.'' I admit that my model is similar with \posscite{Butler1990Gender} theory in some senses, including denying a Cartesian self and supporting a constructed/shaped self-consciousness by the external environment through discursive effect/neuroplasticity. The most significant difference lies in our ontological premise: I believe in an objective reality that exists independently of the human mind \footnote{I admit that it may sound like begging the question, but obviously it's off-topic to provide a sophisticated argument for scientific realism here. }; and for queer theory, our understanding of reality is constructed through discourse and we cannot perceive it without mediation. In most contexts, ontology might be nothing more than a boring metaphysical intellectual game. While in this case, ontology is everything, it decides two completely different strategy.

From a scientific realistic aspect, gender shapes our understanding about the biological, psychological and sociological diversity of human beings, which is inconsistent with its real mathematical structure. This misunderstanding, also known as ``stereotype,'' affects our self-identity. Being analogous to deep learning (connectionism), gender construct is a corrupted training data that contains two flawed classes: Class 0 (female) is consisted of feminine faces, vaginas, clitorises, developed breasts, pink, purple, brooms, mops, kitchens, dolls, stuffed toys, dresses, Mary Jane shoes, jewellery, make-up \ldots~On the contrary, class 1 (male) is made up of masculine faces, penises, testicles, undeveloped breasts, Adam's apples, beards, blue, computers, documents, architecture, toy cars, pants, suits, ties \ldots~An individual's gender identity is the product of it. ``Gender identity'' is our brains desperately trying to find a pattern in a chaotic, nonsensical, and wrongly labelled set of social data. It latches onto these arbitrary connections and creates a rigid internal model that doesn't actually reflect a fundamental reality.

Therefore, the most fundamental ``-centrism'' in our society is not androcentrism, heterocentrism, or cisgender-centrism, but gender-centrism -- an ideology that establishes ``gender'' as the core category for understanding the world and ourselves. By assigning a gender to everything, ``gender'' attempts to bring the entire world under its dominion, to establish itself as the centre of the way humans perceive the world. It prevents humans from accurately perceiving the real mathematical structure of the world. The gender-centrism is so ancient, so deep, that even the most so-called ``liberatory'' theories or social movements -- feminism or LGBTQ -- have not escaped it or do not dare to escape it. They merely try to change cells within the prison. They resist the ``oppression of gender,'' but they are afraid, unwilling, unable, or refuse to resist the existence of ``gender'' itself.

For other socially constructed identities, such as nation, race, class, profession, etc., their supporters clearly know that these identities are socially constructed. Only gender, a completely externally imposed system, is regarded by the entire political spectrum as something \textit{a priori} and essential. The only disagreement is where this essence lies -- in our genitals (``scientific'' gender essentialism), brains (transgender mechanistic materialism), or souls (transgender idealism and religious conservative). It is even regarded by some groups as the ``true self,'' a symbol of ``freedom and empowerment.''

``Gender essence'' or ``gender identity'' is proclaimed by all political camps to be innate, internal, profound, and constitutive of essence, yet it is clearly acquired, social, superficial, and shaped by society and culture. It defines our essence, governs our entire lives, is assigned before the formation of the self identity, and claims to be the self itself. It simultaneously occupies the domains of science, humanities, politics, and religions. \footnote{The ``religion'' refers to the conservative narrative of ``the two sexes are the natural order created by God'' and the liberal narrative of ``a soul born in the wrong body.''} It has a unique, unquestionable, cross-political-spectrum ontological privilege.

% To declare a specific one as our ``core'' self is a questionable assumption. It suppresses the expression of other types of self-identity. The dominant status of ``gender'' over other personality traits and self-identities also reduces the culturally and socially available combinations, leading to a decrease in the freedom of self-expression.

Since the real problem lies in an omni-encompassing ideology that attempts to assign ``gender'' to everything, the most fundamental solution is to abolish the whole gender construct. I hereby propose a solution aiming at abolishing gender by strictly limiting ``sex'' and ``gender'' to atomic entity, detaching them from individuals.

% (\cref{tab:1})
%
%\begin{table}[bt]
%    \caption{Comparison of the Claims and Realities of Gender.}
%    \label{tab:1}
%    % Use "S" column identifier to align on decimal point
%    \begin{tabularx}{\textwidth}{l X X}
%    \toprule
%    Characteristic & Claim          & Reality     \\
%    \midrule
%    Time	& Innate, before self-awareness	& Acquired after learning \\
%    Source	& Internal, in our brains, genitals or souls	& Internalised from society and culture \\
%    Hierarchy	& Profound, equivalent to self-perception	& Superficial, merely a descriptive tool \\
%    Function	& Constitutive of essence, defining existence	& Alienating, psychological colonisation \\
%    Ontological Status	& Cross-political-spectrum ontological privilege	& Arbitrary symbols of language and culture \\
%    Domain	& Science + Humanities + Politics + Religions	& An accidental product of history and culture \\
%    \bottomrule
%    \end{tabularx}
%\end{table}

%Concepts like ``sexual orientation,'' ``gender identity,'' and ``intersex'' were not created to ``liberate humanity from gender binary,'' but to ``protect gender binary from humanity.'' They are just a series of ``epicycles.'' Like the pre-Copernican astronomers, our modern psychologists and sociologists are creating these epicycles for those who do not conform to the norm (homosexuals, bisexuals, transgender people, intersex people). In this way, the system can safely isolate them as ``exceptions,'' thus maintaining the Ptolemaic model (the cisgender heterosexual endosex binary norm) in most situations. The true purpose of historical ``epicycles'' was not to ``help planets find their true orbits,'' but to avoid a radical paradigm shift.
%Otherwise, as we discussed earlier, why does a change intended to increase ``inclusivity'' -- using ``assigned sex'' instead of ``phenotypic sex'' in the definition of transgender -- logically reduce inclusivity and the scope of people who can be considered ``transgender''?
%
%Some zoologists call non-human animal individuals ``gender non-conforming'' (GNC) because their behaviour does not conform to the statistical typic for their own ``phenotypic sex'', such as the female chimpanzee Donna, who occupied territory and fought. Primatologist Frans de Waal even claimed that ``primates are born with a gender identity''~\parencite{DeWaal2022Different, Morin2022Frans}. This is effectively saying that gender is a behavioural characteristic of animals, thereby reducing sociology and psychology to a branch of ethology that specifically studies the species \textit{Homo sapiens}, thus making gender a part of sex.
%
%Thus, if we strictly follow this framework, considering the inaccessibility of subjective experience, ``gender identity'' should be regarded as ``using the vocal cords to produce encoded mechanical waves, or using visual symbols created by the species itself to express oneself as male/female.'' It is a behavioural sexual dimorphism of \textit{Homo sapiens}, which is obviously absurd.
%
%Similarly, under this definition, the sex of sexually monomorphic organisms cannot be determined without dissection. The so-called ``male/female'' that is generally judged based on behavioural characteristics should logically be gender, not sex. A case in point is that many lovebird owners judge their pet birds' ``sex'' based on their behaviour, such as incubation, nest building, and position during mating.
%
%If animal behaviour is gender, then botanists describing the reproductive function of a plant as \textit{gender} is a natural extension of the former. The claim by some transgender activists or the biologists who support them that using the word \textit{gender} to describe plants ``harms'' transgender people~\parencite{Oberle2023Benefits} is baseless. The same word, when used for humans, is a political and human rights issue; when used for great apes, it ``proves the naturalness of transgender''; but when used for plants, it becomes a form of ``harm.'' What is the reason for this distinction? This is essentially anthropocentrism, taxonomic chauvinism, and an act of granting our closest relatives the title of ``honorary humans.''
%
%Moreover, even if we analyse it under the mainstream theory, gender is a sociocultural construct, while gender identity is an individual's internal psychological state. These are two different concepts. ``Society'' and ``culture'' cannot be the object of harm. Claiming that the borrowing of an abstract sociological concept, \textit{gender}, will ``harm'' humans who possess an internal psychological state, \textit{gender identity}, is a category error.
%
%Considering that:
%
%\begin{enumerate}
%    \item Sex is not a natural kind, but a social construct, therefore a part of gender.
%    \item Gender is a behavioural characteristic of animals, therefore a biological attribute.
%\end{enumerate}
%
%Therefore: $ S \subseteq G \wedge G \subseteq S \Rightarrow S = G $
%
%QED\@.
%
%It is clearly demonstrated that no one really knows what the difference between sex and gender is. No one really knows what they are talking about. Different activists and scholars, according to their political needs, arbitrarily borrow concepts from other disciplines and redefine them, completely ignoring whether these acts will cause the entire gender discourse system to collapse logically.
%

The biological sex should be strictly confined to the gametes \parencite{Lehtonen2014Gamete, Goymann2023Biological, Hurst1996There, Griffiths2025Biology}. It is related to, and only to, gametes. Individuals do not have such a sex. Sexual dimorphism is a dynamic spectrum that constantly changes throughout evolutionary history. The so-called ``phenotypic sex'' should be dismantled into a series of discrete, decentralised phenotypic traits such as chromosomes, hormones, as well as all morphology and anatomical traits. They are distributed on the sexual dimorphism spectrum, along with sexually dimorphic traits not traditionally classified as ``phenotypic sex'', like height, weight, body hair, and body fat percentage \parencite{Wells2007Sexual}. Individuals do not have an innate gender; they merely ``possess'' gametes, ``live in''  a society and ``internalise'' the culture.
%The imprecise concept of intersex should be replaced by more detailed terms like intergonadal, intergenital, and sexual intermorphism. Gender should be strictly treated as a sociocultural phenomenon.

By biologically confining sex strictly to an unobservable trait, it cannot be ``assigned'' or ``inferred.'' \textcite{Parvin1982Ovulation} reported a person who was completely ``phenotypic male'' and had fathered a daughter, but one of their two ``testicles'' was actually a pure ovary (not an ovotestis), and dissection showed it had previously ovulated. Therefore, most people, even those who have had children, cannot know for sure if they are capable of producing two types of gametes. This makes it lose any possibility of being used for social classification, discipline, and oppression. It becomes a technical term of reproductive biology, completely ``exiled'' from everyday language and the operation of power.

My proposal is completely different from conservatives, who claim to adopt gametic definition, but still rely on the genital in practice, which is self-contradictory. This even includes some conservative scientists, like \textcite{Sokal2024Sex}, who claim that sex is an ``objective biological reality,'' ``determined at conception and observed at birth.'' I agree that sex \textit{sensu stricto} is a objective biological reality, and is strictly binary in Vertebrata. While according to \textcite{Jones2006Gamete}, ``Conception occurs when a sperm and an ovum fuse to become a zygote.'' ``The process of fertilisation, or conception, involves fusion of the nucleus of a male gamete (sperm) and a female gamete (ovum) to form a new individual.'' At ``conception'' (fertilisation), it is just a zygote, a single cell. It has neither sex \textit{sensu stricto} because it cannot produce its own gametes, nor does it have phenotypic sex by lacking a developed body. Even if its genome will guide it to develop into a typical phenotypic male or female under normal conditions, it will not necessarily be so. For instance, if a 46, XY zygote loses its Y chromosome during the first mitotic division after fertilisation, it will develop into a 45, X0/46, XY chimaera (mixed gonadal dysgenesis) or a 45, X0 individual with Turner syndrome \parencite{Gravholt2017Clinical, Jacobs1997Turner, Lopes2014Mosaicism}.

The binaric sex is still a very useful model in evolutionary biology, ethology, and reproductive ecology. It is obviously technically and ethically impossible to capture and dissect all individual animals to examine the gametes they produce. In these cases, researchers should state in their \textit{Materials and Methods} section what proxy they used to estimate the gamete production capacity and the reliability, such as the situation in birds revealed by \textcite{Hall2025Prevalence}. Sex \textit{sensu stricto} itself is a microscopic reproductive biological trait, not an externally observable morphological character.

%\textcite{Polderman2018Biological} claimed that the heritability of gender identity is 30--60\% and consistent with other behavioural and personality traits, which is a category error. As we have said before, ``gender identity'' cannot be encoded in the genome (this would require extraordinary evidence). We can only have a series of genes related to personality traits, cognitive styles, and body representation. Studying the ``heritability of gender identity'' is a huge logical leap. The correct scientific questions should not be: ``What is the biological basis of gender identity?'' but rather: ``Which heritable biological traits are assigned gender meaning by society and culture?'' (sociology). ``How does the meaning interact with the individual to construct a specific gender identity?'' (psychology). ``What is the biological basis of these traits?'' (genetics and neuroscience). Autism spectrum disorder is also highly heritable \parencite{Sandin2017Heritability}, and autistic traits are higher in those working in STEM fields \parencite{Ruzich2015Sex}. Following \posscite{Polderman2018Biological} methods, we might also be able to calculate a mathematically reasonable number of ``heritability of STEM ability'', which everyone would consider an absurd study. Autistic neurological traits are heritable, while participating in STEM fields is an extremely complex result of innate neurological traits, personal experience, academic training and so on. Biological studies of ``gender identity'' are precisely the 21st-century replication of ``scientific'' racism.

At the social level, all gender concepts and any social constructs should be abolished. The biological characteristics previously considered ``phenotypic sex'' should have no more social significance than height or weight. All mention of gender in laws and regulations should be removed. In cases not involving a relationship, replace "man" or "woman" with "person." In cases involving a relationship (such as marriage), replace them with "one person" and "the other person." Gendered pronouns and titles should be abolished, sexual orientation should be considered mating preferences or aesthetic preferences, gender incongruence should be considered a form of body representation incongruent, and gender-affirming surgery should be considered a form of cosmetic surgery. A person's desire to change their body, whether because of innate body representation incongruence or any acquired factor, is a matter of pure personal freedom. These are merely mechanical modifications to our body, its legitimacy stems from bodily autonomy. It does not need an unprovable ``gender identity'' to justify it. Gender markers should be removed from all nonmedical records, and sex markers in medical records should be multi-level (chromosomes, reproductive organs, fertility, hormone levels, etc.) rather than just male/female. All gender-segregated facilities should be eliminated. Clothing stores should no longer be divided into ``men's/women's'' sections, but organised by clothing type (tops, pants, outerwear) and size/fit. Toys should no longer be divided into ``boys'/girls','' but by function and type (e.g., building blocks, dolls, science experiments, art creation) and appropriate age.

Most importantly, ``gender identity'' should be understood literally, ``identity with a gender,'' which is shaped in one's interaction with and internalisation of social gender constructs. The psychotherapist should play the role of a philosophy and science teacher, promoting self-understanding in clients who are exploring their gender identity through Socratic dialogue. It's not about providing answers; it's about providing tools for thinking and empowering the individual to find their own answers. They are rational beings capable of and deserving of a deep, philosophical engagement with their own identity.

We have no need at all to shy away from ``gender identity is the internalisation of social gender norms and gender stereotypes.'' The gender identity of cisgender people is also the internalisation of gender norms and stereotypes. However, it is politically not important. Why is it a virtue when childhood trauma causes a person to have a strong heart, but when it causes a person to develop an incongruent gender identity, it needs to be ``converted?'' This conservative logic is very easy to refute. What should be emphasised is: gender identity is an acquired psychological state, but it is acquired subtly and unconsciously, like the first language. For the person themselves, it feels very "innate." This is how our brains work, it does not mean that we should blame people for "internalising gender stereotypes."

%This transforms the issue from a special identity under identity politics, a special psychological state (identity), and a specific phenomenon, to the dismantling of an oppressive system. Everyone, whether ``cisgender'' or ``transgender,'' is a victim of this system. It is a political issue that requires the participation of the entire society: why do bathrooms need to be segregated by gender, and why do documents need to be marked with gender?

