%As we said above, if we apply the standards of Aves to Mammalia, we will conclude that almost all humans are intersex. However, in the following argument, let's not jump to such a radical stage.

%Let's first achieve a kind of logical consistency within humanity: individuals with gynaecomastia are intersex. This is the necessary result of applying the standard of breasts as part of ``phenotypic sex'' from other domains to the domain of ``intersex.''

%Then, according to the old diagnostic criteria, like in ICD-10~\parencite{WHO1992ICD10} or DSM-IV-TR~\parencite{APA2000DSM4}, an individual with gynaecomastia who self-identifies as male should be considered a specific kind of transsexual (XtM), because they have ``a sense of discomfort with their anatomic sex,'' and want to make it ``as congruent as possible with one's preferred sex.'' The medical treatment should also be considered ``gender affirming surgery.'' Ironically, both diagnostic criteria explicitly exclude intersex individuals, which is extremely hard to understand.

%However, rather than achieving greater inclusivity by including intersex people, the editors continue to maintain a \textit{de facto} exclusion of intersex people by introducing the concept of  ``assigned sex at birth''~\parencite{APA2013DSM5, WHO2019ICD11}. Not only individuals with gynaecomastia were excluded from transgender, but many traditionally defined

Many concepts in contemporary gender theory are self-contradictory. By introducing the concept of  ``assigned sex at birth''~\parencite{APA2013DSM5, WHO2019ICD11}, some intersex people are excluded from transgender. Let us have a thought experiment: an intersex child is assigned female at birth, but gets lost at a very young age, is reassigned male by adoptive parents, and is raised as a boy. After adulthood, their body is closer to a ``phenotypic male,'' but their gender identity is female. According to the definition of ``assigned sex at birth,'' this individual is a ``cisgender female.''

Ironically, if we use ``phenotypic sex'' to define transgender people, we can capture this individual's unique gender socialisation experience (XtF) very well. Since the so-called ``assigned sex'' is almost always binary in actual medical practice, it simplifies the patterns of children's gender socialisation using two typical phenotypic sexes, replicating the power framework it seeks to oppose, and in fact, brings back the ghost of gender binary.

When we examine ``assigned sex at birth'' more furtherly, we will inevitably ask: Is ``assigned sex/gender at birth'' \footnote{In English, both ``assigned sex'' and ``assigned gender'' are used. } a kind of ``sex'' or ``gender?'' What is the relationship between assigned sex and gender identity?

If gender is unrelated to phenotypic sex and gender identity is not identifying with sex, then logically, being phenotypic or assigned male/female and identifying as male/female are two or three unrelated things. They just share the words ``male/female,'' like the ecological and sociological ``community.''

Therefore, everyone's phenotypic sex (a series of biological characteristics, although artificially selected) or assigned sex at birth (a label on a legal document) is ``inconsistent'' with their gender identity (a psychological state). Or more accurately, it is impossible to discuss whether they are ``consistent'' or ``inconsistent.''. Because they describe three essentially different kinds of things, just as we would not say that the social ``community'' a person belongs to is ``consistent'' with the ecological ``community'' they inhabitant.

Conversely, if those whose assigned sex at birth use the same word as their gender identity are called ``cisgender,'' and their phenotypic sex or assigned sex at birth is ``consistent'' with their gender identity, this means that phenotypic sex and gender are related in some way. Their view on the relationship between sex and gender is not a rigorous philosophical nominalism, but a vulgarised, selectively applied nominalist fallacy. When they need to separate the body from identity, they use nominalism; when they need to establish the cisgender/transgender binary opposition, they secretly retreat to an unreflective realist position.

The conflict between ``nominalism'' and ``realism'' occurs not only between assigned sex at birth and gender identity, but also within ``gender identity'' itself: are the ``woman'' of feminism and the ``woman'' of patriarchy the same concept? The ``woman'' who supports feminism and the traditional ``woman'' both self-identify as ``woman.'' Are their gender identities the same? They claim that all people who identify as ``woman'' share some real, existing ``essence'' called ``female identity'', no matter how different their political stances, lifestyles, and values are. And it uses realist labels like ``cisgender/transgender'' to classify these completely unrelated self-identities as the same kind, simply because their name is or is not consistent with their birth certificate.

Moreover, the cisgender/transgender binary opposition fundamentally violates the ``principle of self-identification,'' because it is equivalent to assigning a gender identity that is ``consistent'' with the assigned sex at birth to all people who have not explicitly identified as a different one. Most ``cisgender'' people have never made such a statement, nor have they ever been asked ``What is your gender identity?'' This act is almost completely isomorphic to the assigned sex at birth; both are top-down, external assignments without consent. A movement, whose important ethical principle is ``opposing non-consensual identity assignment,'' \footnote{\textcite{Butler2025Who}: \ldots Can we decide what being or having a sex means outside of a framework that establishes and reestablishes sex, that is, a framework that has to be imposed with regularity through time, one where the power to self-assign is exercised by those who have already \textit{been} assigned? Some trans people turn against all assignment, claiming that it invariably works in the service of hierarchy.} relies on the non-consensual identity assignment of most people. It repeats the oppressive structure it criticises, but only packaging itself in a ``critical'' language.

It implicitly introduces an \textit{a priori} assumption that ``everyone has a gender identity,'' because the definition of ``cisgender/transgender'' depends on the existence of ``gender identity'' and its ``consistency'' with ``assigned sex at birth.'' By establishing a classification based on ``gender identity,'' it made ``having a gender identity'' a necessary condition for being a complete-socialised person. If you are not ``transgender,'' then you must be ``cisgender'' -- humans are deprived of the options ``I don't have this thing at all,'' ``null,'' or ``undefined.'' Under this framework, the position of ``I have no gender identity'' becomes invisible or politically incorrect. Individuals are deprived of the right to ``quit the game''; they are either ``cisgender'' or ``transgender.'' \footnote{This topic reminds me that I once intended to declare my gender identity as null. I was using it in a very sincere, technical sense (value unassigned). Nevertheless, I immediately realised that I cannot express it like how a computer handles null. When someone asks about my gender identity, I cannot directly throw a ``NullPointerException: field \`gender\` not found in object \`user\`'' in their brains. In real life, it is still a textual label. The ``null'' I am writing in this article is four Latin letters, not the technical null.}

Most fatally, when they set ``cisgender'' as a synonym for ``non-transgender'' or ``having not stated their gender identity,'' they are saying that all transgender people are cisgender at birth. This is equivalent to saying that ``transgender people were cisgender and changed for specific reasons,'' which becomes the conservative viewpoint. This flaw is logically and politically devastating.

For other socially constructed identities, such as nation, race, class, profession, etc., their supporters clearly know that these identities are socially constructed. No black civil rights activist would say that ``black people is a valid taxon, a monophyletic group in phylogeny.'' On the contrary, this is the ``scientific'' racist view that they completely deny. Any modern state, no matter how much it promotes patriotism and loyalty, or the long history and great spirit of the nation, it does not claim to be \textit{a priori} metaphysical ``form'' or ``created by god.'' They all clearly recognise that their country was formed through certain history. Almost no one would use ``natural'' or ``innate'' to defend them.

Only gender, a completely externally imposed system, is regarded by the entire political spectrum as something \textit{a priori} and essential. The only disagreement is where this essence lies -- in our genitals (``scientific'' gender essentialism), brains (transgender mechanism materialism), or souls (transgender idealism and religious conservative). It is even regarded by some groups as the ``true self,'' a symbol of ``freedom and empowerment.''

``Gender essence'' or ``gender identity'' is proclaimed by all political camps to be innate, internal, profound, and constitutive of essence, yet it is clearly acquired, social, superficial, and shaped by society and culture. It defines our essence, governs our entire lives, is assigned before the formation of the self identity, and claims to be the self itself. It simultaneously occupies the domains of science, humanities, politics, and religions. \footnote{The ``religion'' refers to the conservative narrative of ``the two sexes are the natural order created by God'' and the liberal narrative of ``a soul born in the wrong body.''} It enjoys a unique, unquestionable, cross-political-spectrum irrational ontological privilege. (\cref{tab:1})

\begin{table}[bt]
    \caption{Comparison of the Claims and Realities of Gender Discourse.}
    \label{tab:1}
    % Use "S" column identifier to align on decimal point
    \begin{tabularx}{\textwidth}{l X X}
    \toprule
    Characteristic & Claim          & Reality     \\
    \midrule
    Time	& Innate, before self-awareness	& Acquired after learning \\
    Source	& Internal, in our brains, genitals or souls	& Internalised from society and culture \\
    Hierarchy	& Profound, equivalent to self-perception	& Superficial, merely a descriptive tool \\
    Function	& Constitutive of essence, defining existence	& Alienating, psychological colonisation \\
    Ontological Status	& Cross-political-spectrum ontological privilege	& Arbitrary symbols of language and culture \\
    Domain	& Science + Humanities + Politics + Religions	& An accidental product of history and culture \\
    \bottomrule
    \end{tabularx}
\end{table}

The number of words used to describe personality traits and self-identity is at least in the thousands~\parencite{Allport1936Trait}, and their combinations can produce an exponential explosion. To declare a specific one as our ``core'' self is a questionable assumption. It suppresses the expression of other types of self-identity. The dominant status of ``gender'' over other personality traits and self-identities also reduces the culturally and socially available combinations, leading to a decrease in the freedom of self-expression.

Therefore, the most fundamental ``-centrism'' in our society is not androcentrism, heterocentrism, or cisgender-centrism, but gender-centrism -- an ideology that establishes ``gender'' as the core category for understanding the world and ourselves. By assigning a gender to everything, ``gender'' attempts to bring the entire world under its dominion, to establish itself as the centre of the universe, to take over the way humans perceive the world.

It is so ancient, so deeply, that even the most so-called ``liberatory'' theories or social movements -- feminism or LGBTQ -- have not escaped it or do not dare to escape it. They merely try to change cells within the prison. They resist the ``oppression of gender,'' but they are afraid, unwilling, unable, or refuse to resist the dominant position of ``gender'' itself.

Concepts like ``sexual orientation,'' ``gender identity,'' and ``intersex'' were not created to ``liberate humanity from gender binary,'' but to ``protect gender binary from humanity.'' They are just a series of ``epicycles.'' Like the pre-Copernican astronomers, our modern psychologists and sociologists are creating these epicycles for those who do not conform to the norm (homosexuals, bisexuals, transgender people, intersex people). In this way, the system can safely isolate them as ``exceptions,'' thus maintaining the Ptolemaic model (the cisgender heterosexual endosex binary norm) in most situations. The true purpose of historical ``epicycles'' was not to ``help planets find their true orbits,'' but to avoid a radical paradigm shift.
%Otherwise, as we discussed earlier, why does a change intended to increase ``inclusivity'' -- using ``assigned sex'' instead of ``phenotypic sex'' in the definition of transgender -- logically reduce inclusivity and the scope of people who can be considered ``transgender''?
%
%Some zoologists call non-human animal individuals ``gender non-conforming'' (GNC) because their behaviour does not conform to the statistical typic for their own ``phenotypic sex'', such as the female chimpanzee Donna, who occupied territory and fought. Primatologist Frans de Waal even claimed that ``primates are born with a gender identity''~\parencite{DeWaal2022Different, Morin2022Frans}. This is effectively saying that gender is a behavioural characteristic of animals, thereby reducing sociology and psychology to a branch of ethology that specifically studies the species \textit{Homo sapiens}, thus making gender a part of sex.
%
%Thus, if we strictly follow this framework, considering the inaccessibility of subjective experience, ``gender identity'' should be regarded as ``using the vocal cords to produce encoded mechanical waves, or using visual symbols created by the species itself to express oneself as male/female.'' It is a behavioural sexual dimorphism of \textit{Homo sapiens}, which is obviously absurd.
%
%Similarly, under this definition, the sex of sexually monomorphic organisms cannot be determined without dissection. The so-called ``male/female'' that is generally judged based on behavioural characteristics should logically be gender, not sex. A case in point is that many lovebird owners judge their pet birds' ``sex'' based on their behaviour, such as incubation, nest building, and position during mating.
%
%If animal behaviour is gender, then botanists describing the reproductive function of a plant as \textit{gender} is a natural extension of the former. The claim by some transgender activists or the biologists who support them that using the word \textit{gender} to describe plants ``harms'' transgender people~\parencite{Oberle2023Benefits} is baseless. The same word, when used for humans, is a political and human rights issue; when used for great apes, it ``proves the naturalness of transgender''; but when used for plants, it becomes a form of ``harm.'' What is the reason for this distinction? This is essentially anthropocentrism, taxonomic chauvinism, and an act of granting our closest relatives the title of ``honorary humans.''
%
%Moreover, even if we analyse it under the mainstream theory, gender is a sociocultural construct, while gender identity is an individual's internal psychological state. These are two different concepts. ``Society'' and ``culture'' cannot be the object of harm. Claiming that the borrowing of an abstract sociological concept, \textit{gender}, will ``harm'' humans who possess an internal psychological state, \textit{gender identity}, is a category error.
%
%Considering that:
%
%\begin{enumerate}
%    \item Sex is not a natural kind, but a social construct, therefore a part of gender.
%    \item Gender is a behavioural characteristic of animals, therefore a biological attribute.
%\end{enumerate}
%
%Therefore: $ S \subseteq G \wedge G \subseteq S \Rightarrow S = G $
%
%QED\@.
%
%It is clearly demonstrated that no one really knows what the difference between sex and gender is. No one really knows what they are talking about. Different activists and scholars, according to their political needs, arbitrarily borrow concepts from other disciplines and redefine them, completely ignoring whether these acts will cause the entire gender discourse system to collapse logically.
%
