During this time, I was in a state of confused self-exploration, mostly treating it as a meaningless fantasy. Of course, I had wondered if I was ``transgender'' and tried to understand mainstream transgender narratives. However, I kept encountering serious barriers to very basic questions, such as: What is gender identity? Where does it come from? What is its relationship to ``gender''? Why is it ``gendered''?

The term ``gender'' in ``gender identity'' refers to a sociocultural category. If ``gender identity'' is an identity with gender, then it essentially becomes an identity with a social construct. This is logically inconsistent with the idea of an ``innate, profound feeling,'' because social norms are nurtured. It is also politically problematic, as it seems to advocate that people should identify with and internalise the gender roles that ought to be critiqued and deconstructed. If it points to phenotypic sex, this contradicts the distinction between sex/gender in mainstream theory. Moreover, if sex and gender are two independent concepts, how does an identity with gender lead to a desire for bodily modification (sex)?

If the ``gender'' here does not refer to social gender, then what exactly is it? If it refers to gender identity itself, this constitutes a tautology, i.e., ``gender identity is an identity with gender identity,'' which is invalid as a definition.

It is unable to tell me, in an objective, clear, and independently verifiable way, what the ``gender'' in ``gender identity'' means.

Therefore, I concluded that this theory was intellectually unsatisfying. I quickly abandoned it and returned to my original explanation: this was just a meaningless fantasy.

For a long time afterwards, I continued this ``meaningless fantasy,'' but it increasingly affected my life. The most serious issue was that I would cast myself in the role of the female protagonist when reading some adult stories, and sometimes I couldn't distinguish between fantasy and reality. A few months ago, I was reading an adult story about psychological manipulation. I identified with the manipulated character and, for a long time, did not realise it was a story about psychological manipulation, believing the manipulator was genuinely trying to protect ``me.'' However, when I realised he was manipulating and using ``me,'' I had a severe nightmare. I dreamt that ``I'' was crying and begging him to continue deceiving ``me.'' I woke up from the dream in the middle of the night and sat in my room for a long time, unable to fall back asleep.

The next day, I realised I had to take this matter seriously. I initially intended to continue learning about mainstream theories, so I tried to organise all my questions clearly. This included the ambiguity of the sex/gender distinction, the circular reasoning behind ``gender identity'' and ``brain sex,'' and how the current mainstream narrative overemphasises European-American culture and Indo-European languages (e.g., the impact on languages without gendered pronouns), thereby forming a cultural invasion of other cultures. I posted this in a gender-related community, hoping for some advice, help, or response.

What I couldn't understand was that almost no one responded to me seriously. I even doubt they read my post carefully. ``Nobody is interested in reading your AI-generated bullshit.'' ``You just need to post the AI prompt you used.'' ``He is probably a 14-year-old incel who just told ChatGPT to write him an essay promoting gender essentialism.'' I argued with them for a long time, repeatedly telling them, ``This is not AI-generated; I wrote it very seriously,'' and ``If you ask ChatGPT to write an essay promoting gender essentialism and get this result, it only proves that ChatGPT is lying to you.''

I tried to explain to them, ``We might have some misunderstandings,'' but they seemed to refuse to accept it. This ultimately led to my account being banned. I was both angry and disappointed. However, beyond that, the more crucial matter was to solve my own problem.